---
title: "NewYears"
output:
  pdf_document: default
  html_document: default
date: "2023-03-01"
---

***Setup***
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Install packages**
```{r}
# Install package
install.packages("dplyr")
install.packages("tidyverse")
install.packages("scales")
```

**Load packages**
```{r}
# Load packages
library(dplyr)
library(tidyverse)
library(scales)
```

**Set the working directory**
```{r}
# Set the working directory
dir.create('../../src/data-preparation')
```

***Input***
**Load the data**
```{r}
# Define the list of cities and filenames
cities <- c("ams", "london", "paris", "rome")
filenames <- paste0("listings-", cities, ".csv.gz")

# Loop through each city and read in the data
for (i in seq_along(cities)) {
  # Read in the listings data
  assign(paste0("list_", cities[i]), read_csv(filenames[i]))
  
  # Read in the calendar data
  assign(paste0("cal_", cities[i]), read_csv(paste0("calendar-", cities[i], ".csv.gz")))
}
```

***Transformation***
**Summary statistics on the price of the cities for the listings dataset**
```{r}
file_names <- c( 'listings-ams.csv.gz', "listings-london.csv.gz", "listings-paris.csv.gz", "listings-rome.csv.gz")
city_names <- c('Amsterdam', 'London', 'Paris', 'Rome')

# Loop through the file names and perform the same operations on each file
for (i in 1:length(file_names)) {
  list_data <- read_csv(file_names[i])
  list_prices <- list_data$price[!is.na(list_data$price)]
  list_prices <- as.numeric(gsub("\\$", "", list_prices))
  list_prices_summary <- summary(list_prices)
  print(paste("This is the price summary statistics for", city_names[i], ":" , list_prices_summary))
}
```


```{r}
#removing the dollar sign from the "price" column in the calendar data
city_names <- c("ams", "london", "paris", "rome")

for(city in city_names) {
  assign(paste0("cal_", city), get(paste0("cal_", city)) %>%
           mutate(price = ifelse(!is.na(price), as.numeric(gsub("\\$", "", price)), price)))
}
```

**Summary statistics for beds per city**
```{r, echo=FALSE}
# Create a list of the cities
cities_list <- list(list_ams, list_london, list_paris, list_rome)

# Loop
for (i in 1:length(cities_list)) {
  cat("Summary statistics for", city_names[i], "\n")
  cat("Beds\n")
  print(summary(cities_list[[i]]$beds))
}
```


**Subset of the listings dataset for all cities**
```{r, echo=FALSE}
#subset lists of the city from the listing data
subset_list_ams <- data.frame(
  id = list_ams$id,
  host_id = list_ams$host_id,
  host_location = list_ams$host_location,
  neighbourhood = list_ams$neighbourhood,
  room_type = list_ams$room_type,
  price = list_ams$price,
  minimum_nights = list_ams$minimum_nights,
  city = "Amsterdam"
)

subset_list_london <- data.frame(
  id = list_london$id,
  host_id = list_london$host_id,
  host_location= list_london$host_location,
  neighbourhood = list_london$neighbourhood,
  room_type = list_london$room_type,
  price = list_london$price,
  minimum_nights = list_london$minimum_nights,
  city = "London"
)

subset_list_paris <- data.frame(
  id = list_paris$id,
  host_id = list_paris$host_id,
  host_location = list_paris$host_location,
  neighbourhood = list_paris$neighbourhood,
  room_type = list_paris$room_type,
  price = list_paris$price,
  minimum_nights = list_paris$minimum_nights,
  
  city = "Paris")

subset_list_rome <- data.frame(
  id = list_rome$id,
  host_id = list_rome$host_id,
  host_location = list_rome$host_location,
  neighbourhood = list_rome$neighbourhood,
  room_type = list_rome$room_type,
  price = list_rome$price,
  minimum_nights = list_rome$minimum_nights,
  city = "Rome")

total_list <- rbind(subset_list_ams, subset_list_london, subset_list_paris, subset_list_rome)

```

**Subset of the calendar dataset for all cities**
```{r, echo=FALSE}
##subset lists of the city from the calendar data
subset_cal_ams <- data.frame(
  listing_id = cal_ams$listing_id,
  date = cal_ams$date,
  available = cal_ams$available,
  adjusted_price = cal_ams$adjusted_price,
  price = cal_ams$price,
  minimum_nights = cal_ams$minimum_nights,
  maximum_nights = cal_ams$maximum_nights,
  city = "Amsterdam"
)

subset_cal_london <- data.frame(
  listing_id = cal_london$listing_id,
  date = cal_london$date,
  available = cal_london$available,
  adjusted_price = cal_london$adjusted_price,
  price = cal_london$price,
  minimum_nights = cal_london$minimum_nights,
  maximum_nights = cal_london$maximum_nights,
  city = "London"
)

subset_cal_paris <- data.frame(
  listing_id = cal_paris$listing_id,
  date = cal_paris$date,
  available = cal_paris$available,
  adjusted_price = cal_paris$adjusted_price,
  price = cal_paris$price,
  minimum_nights = cal_paris$minimum_nights,
  maximum_nights = cal_paris$maximum_nights,
  city = "Paris"
)

subset_cal_rome <- data.frame(
  listing_id = cal_rome$listing_id,
  date = cal_rome$date,
  available = cal_rome$available,
  adjusted_price = cal_rome$adjusted_price,
  price = cal_rome$price,
  minimum_nights = cal_rome$minimum_nights,
  maximum_nights = cal_rome$maximum_nights,
  city = "Rome"
)

total_cal <- rbind(subset_cal_ams, subset_cal_london, subset_cal_paris, subset_cal_rome)

```

***Output***
**Number of available rooms per city between the 5th of December 2022 and the 4th of December 2023** 
```{r, echo=FALSE}
total_cal <- total_cal %>% 
  mutate(available = ifelse(available == TRUE, "available", available)) %>%
  mutate(available = ifelse(available == FALSE, "unavailable", available))

table(total_cal$available,  total_cal$city)
```

**Number of rooms types per city**
```{r, echo=FALSE}
table(total_list$room_type, total_list$city)
```

**Percentage number of rooms in Amsterdam**
```{r, echo=FALSE}
Amsterdam <- table(list_ams$room_type)
prop.table(Amsterdam)
```

**Percentage number of rooms in London**
```{r, echo=FALSE}
London <- table(list_london$room_type)
prop.table(London)
```

**Percent number of rooms in Paris**
```{r, echo=FALSE}
Paris <- table(list_paris$room_type)
prop.table(Paris)
```

**Percent number of rooms in Rome**
```{r, echo=FALSE}
Rome <- table(list_rome$room_type)
prop.table(Rome)
```

**Airbnb room types offered in Amsterdam**
```{r, echo=FALSE}
piepercent_ams<- round(100*table(list_ams$room_type)/sum(table(list_ams$room_type)), 1)
pie(table(list_ams$room_type), labels = paste0(piepercent_ams, "%"), main = "Room types in Amsterdam", col = rainbow(length(table(list_ams$room_type)), s = 0.5))
legend("bottomleft", c("Entire home/apt","Hotel room","Private room","Shared room"), cex = 0.8,
       fill = rainbow(length(table(list_ams$room_type)), s = 0.5))
```

**Airbnb room types offered in London**
```{r, echo=FALSE}
piepercent_london<- round(100*table(list_london$room_type)/sum(table(list_london$room_type)), 1)
pie(table(list_london$room_type), labels = paste0(piepercent_london, "%"), main = "Room types in London", col = rainbow(length(table(list_london$room_type)), s = 0.5))
legend("bottomright", c("Entire home/apt","Hotel room","Private room","Shared room"), cex = 0.8,
       fill = rainbow(length(table(list_london$room_type)), s = 0.5))
```

**Airbnb room types offered in Paris**
```{r, echo=FALSE}
piepercent_paris<- round(100*table(list_paris$room_type)/sum(table(list_paris$room_type)), 1)
pie(table(list_paris$room_type), labels = paste0(piepercent_paris, "%"), main = "Room types in Paris", col = rainbow(length(table(list_paris$room_type)), s = 0.5))
legend("bottomleft", c("Entire home/apt","Hotel room","Private room","Shared room"), cex = 0.8,
       fill = rainbow(length(table(list_paris$room_type)), s = 0.5))
```

**Airbnb room types offered in Rome**
```{r, echo=FALSE}
piepercent_rome<- round(100*table(list_rome$room_type)/sum(table(list_rome$room_type)), 1)
pie(table(list_rome$room_type), labels = paste0(piepercent_rome, "%"), main = "Room types in Rome", col = rainbow(length(table(list_rome$room_type)), s = 0.5))
legend("topright", c("Entire home/apt","Hotel room","Private room","Shared room"), cex = 0.8,
       fill = rainbow(length(table(list_rome$room_type)), s = 0.5))
```

**Quantity of type of rooms in Amsterdam**
```{r, echo=FALSE}
ggplot(list_ams, aes(x = room_type)) +
  geom_bar(aes(fill = room_type), position = "dodge") +
  ggtitle("Amsterdam") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Type of room", y = "Number of rooms", fill = "Type of room") +
  scale_fill_viridis_d()
```

**Quantity of type of rooms in London**
```{r, echo=FALSE}
ggplot(list_london, aes(x = room_type)) +
  geom_bar(aes(fill = room_type), position = "dodge") +
  ggtitle("London") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Type of room", y = "Number of rooms", fill = "Type of room") +
  scale_fill_viridis_d()
```

**Quantity of type of rooms in Paris**
```{r, echo=FALSE}
ggplot(list_paris, aes(x = room_type)) +
  geom_bar(aes(fill = room_type), position = "dodge") +
  ggtitle("Paris") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Type of room", y = "Number of rooms", fill = "Type of room") +
  scale_fill_viridis_d()
```

**Quantity of type of rooms in Rome**
```{r, echo=FALSE}
ggplot(list_rome, aes(x = room_type)) +
  geom_bar(aes(fill = room_type), position = "dodge") +
  ggtitle("Rome") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Type of room", y = "Number of rooms", fill = "Type of room") +
  scale_fill_viridis_d()
```

**Percentage of rooms offered in Amsterdam**
```{r, echo=FALSE}
ggplot(list_ams, aes(x = room_type)) +
  geom_bar(aes(y = (..count..)/sum(..count..), fill = room_type), position = "dodge") +
  ggtitle("Amsterdam") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Type of room", y = "Number of rooms", fill = "Type of room") +
  scale_fill_viridis_d() +
  scale_y_continuous(labels = scales::percent_format(), name = "Percentage of rooms")
```

**Percentage of rooms offered in London**
```{r, echo=FALSE}
ggplot(list_london, aes(x = room_type)) +
  geom_bar(aes(y = (..count..)/sum(..count..), fill = room_type), position = "dodge") +
  ggtitle("London") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Type of room", y = "Number of rooms", fill = "Type of room") +
  scale_fill_viridis_d() +
  scale_y_continuous(labels = scales::percent_format(), name = "Percentage of rooms")
```

**Percentage of rooms offered in Paris**
```{r, echo=FALSE}
ggplot(list_paris, aes(x = room_type)) +
  geom_bar(aes(y = (..count..)/sum(..count..), fill = room_type), position = "dodge") +
  ggtitle("Paris") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Type of room", y = "Number of rooms", fill = "Type of room") +
  scale_fill_viridis_d() +
  scale_y_continuous(labels = scales::percent_format(), name = "Percentage of rooms")
```

**Percentage of rooms offered in Rome**
```{r, echo=FALSE}
ggplot(list_rome, aes(x = room_type)) +
  geom_bar(aes(y = (..count..)/sum(..count..), fill = room_type), position = "dodge") +
  ggtitle("Rome") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Type of room", y = "Number of rooms", fill = "Type of room") +
  scale_fill_viridis_d() +
  scale_y_continuous(labels = scales::percent_format(), name = "Percentage of rooms")
```

**Number and type of rooms comparison between the cities**
```{r, echo=FALSE}
ggplot(total_list, aes(x = room_type)) +
  geom_bar(aes(fill = room_type), position = "dodge") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  facet_grid(~city) +
  labs(x = "Type of room", y = "Number of rooms", fill = "Type of room") +
  scale_fill_viridis_d()
```
