---
title: "New Year's"
output: html_document
date: "2023-02-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, include=FALSE}
# Install packages
install.packages("dplyr")
install.packages("tidyverse")
install.packages("scales")

# Load packages
library(dplyr)
library(tidyverse)
library(scales)
```

```{r,include = FALSE}
setwd("C:/MA/dPREP/RStudio/Teamproject")

#summary statistics
list_ams <- read_csv('listings-ams.csv.gz')
list_ams_prices <- list_ams$price[!is.na(list_ams$price)]
list_ams_prices <- gsub("\\$", "", list_ams_prices)
list_ams_prices <- as.numeric(list_ams_prices)
list_ams_prices <- summary(list_ams_prices)
list_ams_prices
```

```{r, echo=TRUE}
setwd("C:/MA/dPREP/RStudio/Teamproject")

#summary statistics
list_lon <- read_csv("listings-london.csv.gz") 
list_lon_prices <- list_lon$price[!is.na(list_lon$price)]
list_lon_prices <- gsub("\\$", "", list_lon_prices)
list_lon_prices <- as.numeric(list_lon_prices)
list_lon_prices <- summary(list_lon_prices)
list_lon_prices
```

```{r, echo=TRUE}
setwd("C:/MA/dPREP/RStudio/Teamproject")

#summary statistics
list_par <- read_csv("listings-paris.csv.gz") 
list_par_prices <- list_par$price[!is.na(list_par$price)]
list_par_prices <- gsub("\\$", "", list_par_prices)
list_par_prices <- as.numeric(list_par_prices)
list_par_prices <- summary(list_par_prices)
list_par_prices
```

```{r, echo=TRUE}
setwd("C:/MA/dPREP/RStudio/Teamproject")

#summary statistics
list_rom <- read_csv("listings-rome.csv.gz")
list_rom_prices <- list_rom$price[!is.na(list_rom$price)]
list_rom_prices <- gsub("\\$", "", list_rom_prices)
list_rom_prices <- as.numeric(list_rom_prices)
list_rom_prices <- summary(list_rom_prices)
list_rom_prices
```

```{r, echo=FALSE}
# Create a list of the cities
cities_list <- list(list_ams, list_lon, list_par, list_rom)

# Names of the cities
cities_names <- c("Amsterdam", "London", "Paris", "Rome")

# Loop
for (i in 1:length(cities_list)) {
  cat("Summary statistics for", cities_names[i], "\n")
  cat("Beds\n")
  print(summary(cities_list[[i]]$beds))
}

```{r, echo=FALSE}
subset_list_ams <- data.frame(
  id = list_ams$id,
  host_id = list_ams$host_id,
  host_location = list_ams$host_location,
  neighbourhood = list_ams$neighbourhood,
  room_type = list_ams$room_type,
  price = list_ams$price,
  minimum_nights = list_ams$minimum_nights,
  city = "Amsterdam"
)

subset_list_lon <- data.frame(
  id = list_lon$id,
  host_id = list_lon$host_id,
  host_location= list_lon$host_location,
  neighbourhood = list_lon$neighbourhood,
  room_type = list_lon$room_type,
  price = list_lon$price,
  minimum_nights = list_lon$minimum_nights,
  city = "London"
)

subset_list_par <- data.frame(
  id = list_par$id,
  host_id = list_par$host_id,
  host_location = list_par$host_location,
  neighbourhood = list_par$neighbourhood,
  room_type = list_par$room_type,
  price = list_par$price,
  minimum_nights = list_par$minimum_nights,
  
  city = "Paris")

subset_list_rom <- data.frame(
  id = list_rom$id,
  host_id = list_rom$host_id,
  host_location = list_rom$host_location,
  neighbourhood = list_rom$neighbourhood,
  room_type = list_rom$room_type,
  price = list_rom$price,
  minimum_nights = list_rom$minimum_nights,
  city = "Rome")

total_list <- rbind(subset_list_ams, subset_list_lon, subset_list_par, subset_list_rom)
```

```{r, echo=FALSE}
table(total_list$room_type, total_list$city)
```

```{r, echo=FALSE}
Amsterdam <- table(list_ams$room_type)
prop.table(Amsterdam)
```

```{r, echo=FALSE}
London <- table(list_lon$room_type)
prop.table(London)
```

```{r, echo=FALSE}
Paris <- table(list_par$room_type)
prop.table(Paris)
```

```{r, echo=FALSE}
Rome <- table(list_rom$room_type)
prop.table(Rome)
```

```{r, echo=FALSE}
piepercent_ams<- round(100*table(list_ams$room_type)/sum(table(list_ams$room_type)), 1)
pie(table(list_ams$room_type), labels = paste0(piepercent_ams, "%"), main = "Room types in Amsterdam", col = rainbow(length(table(list_ams$room_type)), s = 0.5))
legend("bottomleft", c("Entire home/apt","Hotel room","Private room","Shared room"), cex = 0.8,
       fill = rainbow(length(table(list_ams$room_type)), s = 0.5))
```

```{r, echo=FALSE}
piepercent_lon<- round(100*table(list_lon$room_type)/sum(table(list_lon$room_type)), 1)
pie(table(list_lon$room_type), labels = paste0(piepercent_lon, "%"), main = "Room types in London", col = rainbow(length(table(list_lon$room_type)), s = 0.5))
legend("bottomright", c("Entire home/apt","Hotel room","Private room","Shared room"), cex = 0.8,
       fill = rainbow(length(table(list_lon$room_type)), s = 0.5))
```

```{r, echo=FALSE}
piepercent_par<- round(100*table(list_par$room_type)/sum(table(list_par$room_type)), 1)
pie(table(list_par$room_type), labels = paste0(piepercent_par, "%"), main = "Room types in Paris", col = rainbow(length(table(list_par$room_type)), s = 0.5))
legend("bottomleft", c("Entire home/apt","Hotel room","Private room","Shared room"), cex = 0.8,
       fill = rainbow(length(table(list_par$room_type)), s = 0.5))
```

```{r, echo=FALSE}
piepercent_rom<- round(100*table(list_rom$room_type)/sum(table(list_rom$room_type)), 1)
pie(table(list_rom$room_type), labels = paste0(piepercent_rom, "%"), main = "Room types in Rome", col = rainbow(length(table(list_rom$room_type)), s = 0.5))
legend("topright", c("Entire home/apt","Hotel room","Private room","Shared room"), cex = 0.8,
       fill = rainbow(length(table(list_rom$room_type)), s = 0.5))
```

```{r, echo=FALSE}
ggplot(list_ams, aes(x = room_type)) +
  geom_bar(aes(fill = room_type), position = "dodge") +
  ggtitle("Amsterdam") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Type of room", y = "Number of rooms", fill = "Type of room") +
  scale_fill_viridis_d()
```

```{r, echo=FALSE}
ggplot(list_lon, aes(x = room_type)) +
  geom_bar(aes(fill = room_type), position = "dodge") +
  ggtitle("London") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Type of room", y = "Number of rooms", fill = "Type of room") +
  scale_fill_viridis_d()
```

```{r, echo=FALSE}
ggplot(list_par, aes(x = room_type)) +
  geom_bar(aes(fill = room_type), position = "dodge") +
  ggtitle("Paris") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Type of room", y = "Number of rooms", fill = "Type of room") +
  scale_fill_viridis_d()
```

```{r, echo=FALSE}
ggplot(list_rom, aes(x = room_type)) +
  geom_bar(aes(fill = room_type), position = "dodge") +
  ggtitle("Rome") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Type of room", y = "Number of rooms", fill = "Type of room") +
  scale_fill_viridis_d()
```

```{r, echo=FALSE}
ggplot(list_ams, aes(x = room_type)) +
  geom_bar(aes(y = (..count..)/sum(..count..), fill = room_type), position = "dodge") +
  ggtitle("Amsterdam") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Type of room", y = "Number of rooms", fill = "Type of room") +
  scale_fill_viridis_d() +
  scale_y_continuous(labels = scales::percent_format(), name = "Percentage of rooms")
```

```{r, echo=FALSE}
ggplot(list_lon, aes(x = room_type)) +
  geom_bar(aes(y = (..count..)/sum(..count..), fill = room_type), position = "dodge") +
  ggtitle("London") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Type of room", y = "Number of rooms", fill = "Type of room") +
  scale_fill_viridis_d() +
  scale_y_continuous(labels = scales::percent_format(), name = "Percentage of rooms")
```

```{r, echo=FALSE}
ggplot(list_par, aes(x = room_type)) +
  geom_bar(aes(y = (..count..)/sum(..count..), fill = room_type), position = "dodge") +
  ggtitle("Paris") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Type of room", y = "Number of rooms", fill = "Type of room") +
  scale_fill_viridis_d() +
  scale_y_continuous(labels = scales::percent_format(), name = "Percentage of rooms")
```

```{r, echo=FALSE}
ggplot(list_rom, aes(x = room_type)) +
  geom_bar(aes(y = (..count..)/sum(..count..), fill = room_type), position = "dodge") +
  ggtitle("Rome") +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(x = "Type of room", y = "Number of rooms", fill = "Type of room") +
  scale_fill_viridis_d() +
  scale_y_continuous(labels = scales::percent_format(), name = "Percentage of rooms")
```

```{r, echo=FALSE}
ggplot(total_list, aes(x = room_type)) +
  geom_bar(aes(fill = room_type), position = "dodge") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  facet_grid(~city) +
  labs(x = "Type of room", y = "Number of rooms", fill = "Type of room") +
  scale_fill_viridis_d()
```








